HO unification from object language to meta language

### 2024-02-19 paper/main.tex
updates compile
Some typos

\documentclass[sigconf]{acmart}

\usepackage{myTools}
% \addbibresource{bib.bib}
\usepackage{macros}

@@

for example here

@@

A natural encoding (others are discussed section xx)
uses c for constants, all for forall, and then app and lam
for the lambda calculus part.

@@

unfortunately this does not work since the last rule cannt
backchain on the encoded goal

\begin{elpicode}
decision (all (app[c"fin",c"7"]) y\ app[c"nfact", y, c"3"])
\end{elpicode}

@@

\begin{elpicode}
app[c"nfact", y, c"3"] = app[P, y]
\end{elpicode}

in this paper we study a more sophisticated encoding

@@

our choice of encoding of DTT may look weird to the reader familiar with
LF, since used a shallow encoding of classes and binders, but not of the
``lambda calculus'' part of DTT. Here a more lightweight encoding
that unfortunately does not fit our use case

@@

moreover we use the same encoding for meta programming, or even just to provide
hand written rules. We want to access the syntax of OL, so our embedding cannot
be that shallow. We want to keep it shallow for the binders, but we need
a c, app and lam nodes.

another alternative

@@

gives up all half of what the ML gives us. moreover even if unif here embodies
he eq theory of DTT which is much stringer than the on of ML, we don't need 
it. according to our experience eta beta suffice, but HO is needed.

@@

\noindent %
\begin{tabular}{c|c}
  \begin{minipage}[c]{0.50\linewidth}
    \begin{elpicode}
      kind term type.
      type const gref -> term.
      type app list term -> term.
      type fun (term -> term) -> term.
      type prod (term -> term) -> term.
    \end{elpicode}
  \end{minipage}
  &
  \begin{minipage}[c]{0.48\linewidth}
    \begin{textcode}
      Example:
      a       ==> const `a
      f a     ==> app[const `f, const `a]
      ~$\lambda$~x => x ==> fun x\ x
      ~$\forall$x, F x~ ==> prod x\ app[F, x]
    \end{textcode}
  \end{minipage}
\end{tabular}

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{bib}

>>>>

\documentclass[sigconf,natbib=false]{acmart}
\usepackage[]{biblatex}

\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}
\addbibresource{bib.bib}

\usepackage{myTools}
\usepackage{macros}

@@

\noindent For example here

@@

A natural encoding (others are discussed in section xx)
uses c for constants, all for forall, and then app and lam
for the lambda calculus part.

@@

Unfortunately this does not work since the last rule cannt
backchain on the encoded goal

\begin{elpicode}
decision (all (app[c"fin",c"7"]) y\ app[c"nfact", y, c"3"]).
\end{elpicode}

@@

\begin{elpicode}
app[c"nfact", y, c"3"] = app[P, y].
\end{elpicode}

In this paper we study a more sophisticated encoding

@@

Our choice of encoding of DTT may look weird to the reader familiar with
LF, since used a shallow encoding of classes and binders, but not of the
``lambda calculus'' part of DTT. Here a more lightweight encoding
that unfortunately does not fit our use case

@@

moreover we use the same encoding for meta programming, or even just to provide
hand written rules. We want to access the syntax of OL, so our embedding cannot
be that shallow. We want to keep it shallow for the binders, but we need
the c, app and lam nodes. % all ?

Another alternative

@@

gives up all half of what the ML gives us. Moreover even if unif here embodies
the eq theory of DTT which is much stronger than the one of the ML, we don't need 
it. According to our experience eta beta suffice, but HO is needed.

@@

\noindent %
% \begin{tabular}{c|c}
  \begin{center}
    \begin{minipage}[c]{0.8\linewidth}
      \begin{elpicode}
        kind term type.
        type const gref -> term.
        type app list term -> term.
        type fun (term -> term) -> term.
        type prod (term -> term) -> term.
      \end{elpicode}
    \end{minipage}
  \end{center}

  % &
  % \begin{minipage}[c]{0.48\linewidth}
  %   \begin{textcode}
  %     Example:
  %     a       ==> const `a
  %     f a     ==> app[const `f, const `a]
  %     ~$\lambda$~x => x ==> fun x\ x
  %     ~$\forall$x, F x~ ==> prod x\ app[F, x]
  %   \end{textcode}
  % \end{minipage}
% \end{tabular}

@@

\printbibliography
